Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-23 Paper/Paper.tex
improved
improved, new figure added

% Title.
% ------
\title{Clustering Beat-Chroma Patterns in a Large Music Database}

@@

How was this codebook trained?
What do we expect it to capture?

FIXME: fix the labels in the figure (label pitch class on the y axis,
and maybe only beats [0 2 4 6] on the ax axis, add codeword numbers to
title), etc.

@@

(It is kind of interesting that sustained minor triad is more common
than the major triad (codes 4 and 5 in figure 7).  Don't fear the
reaper is in Amin, could it be related to this?)

@@

@@

@@

As for enhancements, we specifically did not compress our features using
gaussian mixtures or other generative model. That being said, these methods
could be use to develop better distance measures between \textit{Shingles}.
The use of the euclidean distance is arbitrary. Summarizing patches
with gaussians, and then comparing the distance between those gaussians,
could reduce the influence of the noise in the distance measure.

>>>>

% Title.
% ------
\title{Clustering Beat-Chroma Patterns\\ in a Large Music Database}

@@

We train a codebook of size $200$ over patterns of size $12$x$8$ covering
$2$ bars at a time. Results shown are on a second testing set, see
Subsection \ref{ssec:artist}.

@@

@@

Showing codewords of $2$ bars is practical and consistent with our experiments
in Section \ref{sec:exps2}. However, longer codewors can also reveal
interesting structures. A random samples of such codewords is presented
in Figure \ref{fig:codes8bars}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{codes_8bars}
\end{center}
\caption{\small{Sample of longer codewords spanning over $8$ bars. Codewords
selected randomly from a codebook of size $200$. As usual, we see sustained
notes, but also some long-term structures.
}}
\label{fig:codes8bars}
\end{figure}

@@

As for enhancements, we specifically did not compress our features using
gaussian mixtures or other generative model. That being said, these methods
could be use to develop better distance measures between patterns.
The use of the euclidean distance is arbitrary. Summarizing patches
with gaussians, and then comparing the distance between those gaussians,
could reduce the influence of the noise in the distance measure.
